A tool set for random number generation on GPUs in R

### 2021-11-30 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
update paper1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3012 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<setup, cache=FALSE,include=FALSE>>=
library('knitr')

options(continue="+  ",  prompt="R> ", digits=3, width=57)

@@

 <<monthdata,eval=TRUE,echo=FALSE, cache=TRUE, fig.pos='h'>>=
library(knitr)
knitr::kable(month,format="latex", align = c("rrrrrrrrrrrr"), 
  caption = "\\label{tab:month}Monthly birth anomaly data", booktabs=TRUE,linesep = "") %>%
  kable_styling(full_width = F, position = "center")#latex_options = "HOLD_position")
@

@@

<<weekdata, eval=TRUE, echo=FALSE, cache=TRUE>>=
knitr::kable(week,format="latex",align = c("rrrrrrrrrrrr"), caption = "Day-of-week birth anomaly data\\label{tab:week}", booktabs=TRUE,linesep = "") %>%
kable_styling(full_width = F, position = "center")#, latex_options = "HOLD_position")
@

>>>>

<<setup, cache=FALSE,include=FALSE>>=
library('knitr')
options(continue="+  ",  prompt="R> ", digits=3, width=57)

@@

 <<monthdata,eval=TRUE,echo=FALSE, cache=TRUE, fig.pos='h', message=FALSE>>=
library(knitr)
library(tidyverse)
library(kableExtra)
knitr::kable(month,format="latex", align = c("rrrrrrrrrrrr"), #label="tab:month"
  caption = "Monthly birth anomaly data\\label{tab:month}", booktabs=TRUE,linesep = "") %>%
  kable_styling(full_width = F, position = "center")#latex_options = "HOLD_position")
@

@@

<<weekdata, eval=TRUE, echo=FALSE, cache=TRUE>>=
knitr::kable(week,format="latex",align = c("rrrrrrrrrrrr"),  #label = "tab:week",
             caption = "Day-of-week birth anomaly data\\label{tab:week}", booktabs=TRUE,linesep = "") %>%
kable_styling(full_width = F, position = "center")#, latex_options = "HOLD_position")
@

### 2021-11-30 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.tex
update paper1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3012 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We generate a large-size matrix of 100 million double-precision Gaussian random numbers, and compare the run-time between using \fct{stats::rnorm} and \fct{clrng::rnorm}. The best performance we have seen using \fct{clrng::rnorm} is around 120 times faster with $512 \times 128$ work-items than using the \fct{stats::rnorm}. The difference in elapsed time becomes larger when matrix size goes larger.
\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   0.077   0.000   0.076
\end{CodeOutput} 
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   7.103   0.651   7.750
\end{CodeOutput} 
\end{CodeChunk}

@@

Below is an example that produces a matrix of Exponential random numbers with expectation equal to 1.
\begin{CodeChunk}
\begin{CodeOutput}
##       [,1]  [,2]  [,3]  [,4]
## [1,] 0.343 0.364 0.542 0.054
## [2,] 1.113 3.642 0.200 2.770
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   0.316   0.000   0.316
\end{CodeOutput}
\begin{CodeOutput}
## [1] -47955
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1015808
\end{CodeOutput}
\begin{CodeOutput}
## [1] 410825
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.404
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   0.137   0.000   0.137
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.4
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   3.854   0.011   3.864
\end{CodeOutput}
\begin{CodeOutput}
## [1] -54990
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1e+07
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1193
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.000119
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   0.009   0.000   0.009
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.000999
\end{CodeOutput} 
\end{CodeChunk}

\subsection{A summary of the results}
We summarized the comparison results in the table \ref{tab:summary} and plot the test statistics in Figure \ref{fig4}.
\begin{table}

>>>>

We generate a large-size matrix of 100 million double-precision Gaussian random numbers, and compare the run-time between using \fct{stats::rnorm} and \fct{clrng::rnorm}. The best performance we have seen using \fct{clrng::rnorm} is around 120 times faster with $512 \times 128$ work-items than using the \fct{stats::rnorm}. The difference in elapsed time becomes larger when matrix size goes larger.
\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   0.050   0.000   0.051
\end{CodeOutput} 
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   6.599   0.762   7.358
\end{CodeOutput} 
\end{CodeChunk}

@@

Below is an example that produces a matrix of Exponential random numbers with expectation equal to 1.
\begin{CodeChunk}
\begin{CodeOutput}
##       [,1] [,2]   [,3]  [,4]
## [1,] 0.707 1.58 0.1815 0.387
## [2,] 1.131 6.38 0.0157 2.768
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##    0.32    0.00    0.32
\end{CodeOutput}
\begin{CodeOutput}
## [1] -47955
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1015808
\end{CodeOutput}
\begin{CodeOutput}
## [1] 410825
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.404
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##  14.448   0.018  14.457
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.404
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##   1.936   0.005   1.940
\end{CodeOutput}
\begin{CodeOutput}
## [1] -54990
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1e+07
\end{CodeOutput}
\begin{CodeOutput}
## [1] 1193
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.000119
\end{CodeOutput} 
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeOutput}
##    user  system elapsed 
##  89.796   0.107  89.865
\end{CodeOutput}
\begin{CodeOutput}
## [1] 0.000125
\end{CodeOutput} 
\end{CodeChunk}

\subsection{A summary of the results}
We summarized the comparison results in the table \ref{tab:summary} and plot the test statistics in Figure %\ref{fig4}.
\begin{table}
